Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-08-05 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
update paper fitbit

# Bind every tibble that contains "interval_complete" to a new tiblle
df_aoi <- 
  mget(ls(pattern = "interval_complete")) %>%
  bind_rows()

@@

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          starts_with("Time_to_first_fixation"),
          !"Time_to_first_fixation.Disruptive_Person") %>%
  rowwise() %>% 
  transmute(Group = Group,
            Sum_time_fixation = sum(c_across(starts_with("Time_to_first_fixation")
                                                    ),
                                           na.rm = TRUE
                                           ) 
            ) %>% 
  mutate(Group = as_factor(Group)) -> df_ttff_sum

# mean & SD time to first fixation 
# novices
mean_time_nov <- 
  df_ttff_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_time_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_nov <- 
  df_ttff_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_time_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_time_exp <-
  df_ttff_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_time_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_exp <- 
  df_ttff_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_time_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on ALL AOIS
df_ttff_sum %>% 
  ggplot(mapping = aes(x = Group,
                       y = Sum_time_fixation)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to first fixation\non all AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_time_group
plot_time_group

@@

# TIME TO FIRST FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Expert"],
       y = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Novice"])

# TIME TO FIRST FIXATIONS on all AOIs 
# effect size for expertise differences
d_time_all <- CohenD(x = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Expert"],
                    y = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Novice"],
                    na.rm = TRUE)

@@

# changing milliseconds into seconds
df_ttff_disrup$`Time to first fixation in seconds` <-
  round(df_ttff_disrup$Time_to_first_fixation.Disruptive_Person / 1000,
        digits = 2)

##################### plotting time to first fixation for groups ##################### 
fix_group_plot <- 
  ggplot(data = df_ttff_disrup,
         mapping = aes(x = Group,
                       y = `Time to first fixation in seconds`)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  # ylim(0,250) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to First Fixation\non AOI `Disruptive Person`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  )

fix_group_plot

@@

```{r}
##################### plotting time to first fixation for 3 disruptions sum up ##################### 
df_aoi %>%
  select (Group,
          Participant,
          TOI,
          "Time_to_first_fixation.Disruptive_Person") %>% 
  mutate(Group = as_factor(Group)) -> toi_fix

toi_fix$TOI[toi_fix$TOI == "Chatting_with_neighbour" |
              toi_fix$TOI == "Heckling" |
              toi_fix$TOI == "Whispering"] <- "Verbal disruption"

toi_fix$TOI[toi_fix$TOI == "Head_on_table" |
              toi_fix$TOI == "Looking_at_phone" |
              toi_fix$TOI == "Drawing"] <- "Lack of eagerness"

toi_fix$TOI[toi_fix$TOI == "Clicking_pen" |
              toi_fix$TOI == "Drumming_with_hands" |
              toi_fix$TOI == "Snipping_with_fingers"] <- "Agitation"

toi_fix <-
  toi_fix %>% 
  filter(TOI == "Verbal disruption" |
         TOI == "Lack of eagerness"|
         TOI == "Agitation")

# remoce all NAs
toi_fix <- na.omit(toi_fix)

# changing milliseconds into seconds
toi_fix$`Time to first fixation in seconds`<- round(toi_fix$Time_to_first_fixation.Disruptive_Person/1000,
                                                    digits = 2)

# plotting
fix_plot_sum <-
  ggplot(data = toi_fix,
         mapping = aes(x = Group,
                       y = `Time to first fixation in seconds`)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to First Fixation\non AOI `Disruptive Person`\nfor disruption categories") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")) +
  facet_wrap(facets = vars(TOI),
             nrow = 1,
             strip.position = "bottom")

fix_plot_sum

#################### MEAN, SD, N ############

# mean ttff for groups
toi_group_mean <- df_ttff_disrup %>%
  group_by(Group) %>%
  summarise("N"=n_distinct(Participant),
            "M" = round(mean(`Time to first fixation in seconds`), 2),
            "SD" = round(sd(`Time to first fixation in seconds`), 2))

# mean ttff for disrup. categories
toi_mean <- toi_fix %>%
  group_by(Group,
           TOI) %>%
  summarise("N"=n_distinct(Participant),
            "M" = round(mean(`Time to first fixation in seconds`), 2),
            "SD" = round(sd(`Time to first fixation in seconds`), 2))

################ t-test & effect size
# TIME TO FIRST FIXATIONS 
# t-test for expertise differences
t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"])

>>>>

# Bind every tibble that contains "interval_complete" to a new tible
df_aoi <- 
  mget(ls(pattern = "interval_complete")) %>%
  bind_rows()

@@

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          starts_with("Time_to_first_fixation"),
          !"Time_to_first_fixation.Disruptive_Person") %>%
  rowwise() %>% 
  transmute(Group = Group,
            Sum_time_fixation = sum(c_across(starts_with("Time_to_first_fixation")
                                                    ),
                                           na.rm = TRUE
                                           ) 
            ) %>% 
  mutate(Sum_time_fixation_sec = round(Sum_time_fixation/1000,
                                         digits = 0),
         Group = as_factor(Group)
         ) -> df_ttff_sum

# mean & SD time to first fixation 
# novices
mean_time_nov <- 
  df_ttff_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_time_fixation_sec) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_nov <- 
  df_ttff_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_time_fixation_sec) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_time_exp <-
  df_ttff_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_time_fixation_sec) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_exp <- 
  df_ttff_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_time_fixation_sec) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on ALL AOIS
df_ttff_sum %>% 
  ggplot(mapping = aes(x = Group,
                       y = Sum_time_fixation_sec)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to first fixation on all AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_time_group
plot_time_group

@@

# TIME TO FIRST FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Expert"],
       y = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Novice"])

# TIME TO FIRST FIXATIONS on all AOIs 
# effect size for expertise differences
d_time_all <- CohenD(x = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Expert"],
                    y = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Novice"],
                    na.rm = TRUE)

@@

# changing milliseconds into seconds
df_ttff_disrup$Disrup_time_fixation_sec <-
  round(df_ttff_disrup$Time_to_first_fixation.Disruptive_Person / 1000,
        digits = 2)

# mean & SD time to first fixation "Disruptive Person"
# novices
mean_time_disrup_nov <- 
  df_ttff_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Disrup_time_fixation_sec) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_disrup_nov <- 
  df_ttff_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Disrup_time_fixation_sec) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_time_disrup_exp <-
  df_ttff_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Disrup_time_fixation_sec) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_disrup_exp <- 
  df_ttff_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Disrup_time_fixation_sec) %>% 
  sd() %>% 
  round(., digits = 0)

##################### plotting time to first fixation for groups ##################### 
plot_time_disrup <- 
  ggplot(data = df_ttff_disrup,
         mapping = aes(x = Group,
                       y = Disrup_time_fixation_sec)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  # ylim(0,250) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to First Fixation\non AOI `Disruptive Person`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  )

plot_time_disrup

# saving plot
ggsave(plot = plot_time_disrup,
       filename = "plots/plot_time_disrup.svg",
       height = 8,
       width = 8,
       units = "in")

# TIME TO FIRST FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"])

# TIME TO FIRST FIXATIONS on all AOIs 
# effect size for expertise differences
d_time_all <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
                    y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
                    na.rm = TRUE)

@@

```{r}
# filter relevant rows and columns

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          "Time_to_first_fixation.Anna",
          "Time_to_first_fixation.Bianca",
          "Time_to_first_fixation.Carl(a)") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Stud_time_fixation = sum(c_across(starts_with("Time_to_first_fixation")
                                                 ),
                                         na.rm = TRUE
                                         )
            ) %>% 
  mutate(Stud_time_fixation_sec = round(Stud_time_fixation/1000, 
                                  digits = 0),
         Group = as_factor(Group)) -> df_ttff_stud

# mean & SD time to first fixation "Disruptive Person"
# novices
mean_time_stud_nov <- 
  df_ttff_stud %>%
  filter(Group == "Novice") %>% 
  pull(Stud_time_fixation_sec) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_stud_nov <- 
  df_ttff_stud %>%
  filter(Group == "Novice") %>% 
  pull(Stud_time_fixation_sec) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_time_stud_exp <-
  df_ttff_stud %>%
  filter(Group == "Expert") %>% 
  pull(Stud_time_fixation_sec) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_stud_exp <- 
  df_ttff_stud %>%
  filter(Group == "Expert") %>% 
  pull(Stud_time_fixation_sec) %>% 
  sd() %>% 
  round(., digits = 0)

##################### plotting time to first fixation for AOI students ##################### 
plot_time_stud <- 
  ggplot(data = df_ttff_stud,
         mapping = aes(x = Group,
                       y = Stud_time_fixation_sec)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  # ylim(0,250) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to First Fixation\non AOI `Students`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  )

plot_time_stud

# saving plot
ggsave(plot = plot_time_stud,
       filename = "plots/plot_time_stud.svg",
       height = 8,
       width = 8,
       units = "in")

# TIME TO FIRST FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Expert"],
       y = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Novice"])

# TIME TO FIRST FIXATIONS on all AOIs 
# effect size for expertise differences
d_time_all <- CohenD(x = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Expert"],
                    y = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Novice"],
                    na.rm = TRUE)
```

### 2022-08-05 02_paper/02_study/01_eye tracking video questionnaire paper/paper_methods.tex
update paper fitbit

@@

>>>>

\begin{lltable}

\begin{TableNotes}[para]
\normalsize{\textit{Note.} Item scores are summed. Women who score 3+ and men who score 4+ are at-risk}
\end{TableNotes}

\begin{longtable}{m{8cm}m{2cm}m{2cm}m{2cm}m{2cm}m{2cm}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:reaction_codingsystem}AUDIT-C scoring table}\\
\toprule
 & \multicolumn{5}{c}{Score} \\
\cmidrule(r){2-6}
Questions & \multicolumn{1}{c}{0} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:reaction_codingsystem} continued}}\\
\toprule
 & \multicolumn{5}{c}{Score} \\
\cmidrule(r){2-6}
Questions & \multicolumn{1}{c}{0} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4}\\
\midrule
\endhead
How often do you have a drink containing alcohol? & Never & Monthly or less & 2-4 times per month & 2-3 times per week & 4+ times per week\\
How many standard drinks of alcohol do you drink on a typical day when you are drinking? & 1–2 & 3-4 & 5-6 & 7-9 & 10+\\
How often do you have 5 or more drinks on one occasion? & Never & Less than monthly & monthly & Weekly & Daily or almost daily\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

\end{lltable}

@@

XXX FRANZI
